Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-16 robdml.tex
tex
p1

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to security implications of adversarial vulnerability, adversarial
	robustness of deep metric learning models has to be improved.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing defenses dismiss the min-max adversarial training, but instead
	learn from a weak adversary inefficiently.
	% our starting point
	Conversely, we propose Hardness Manipulation to efficiently perturb the
	training triplet till a specified level of hardness for adversarial
	training, according to a harder benign triplet or a pseudo-hardness
	function.
	% merit
	It is flexible since regular training and min-max adversarial training
	are its boundary cases.
	% GA Adversary
	Besides, Gradual Adversary, a family of pseudo-hardness functions is
	proposed to gradually increase the specified hardness level during training
	for a better balance between performance and robustness.
	% Intra-Class Structure
	Additionally, an Intra-Class Structure loss term among benign and adversarial
	examples further improves training efficiency and model robustness.
	% Experiment and Conclusion
	Comprehensive experimental results suggest that the proposed method,
	although simple in its form, overwhelmingly outperforms the
	state-of-the-art defenses in terms of training cost,
	robustness, as well as performance on benign examples.
%
\end{abstract}

@@

Existing defense methods~\cite{advrank,robrank} are adversarial training-based,
inspired by Madry's \emph{min-max} adversarial training~\cite{madry} because it
is consistently one of the most effective methods for classification task.
%
Specifically, Madry's method involves a inner problem to \emph{maximize} the
loss by perturbing the inputs into adversarial examples, and an outer problem
to \emph{minimize} the loss by updating the model parameters.
%
However, in order to avoid model collapse due to excessively hard examples, the
existing defenses refrain from directly adopting such min-max paradigm, but
instead replace the inner problem to indirectly increase the loss value to a
certain level, which suffers from low efficiency and weak adversary (and hence
weak robustness).
%
Since training cost is already a serious issue of adversarial training, the
efficiency in gaining higher adversarial robustness under a lower budget is
inevitable and important for DML defense.

@@

\textbf{Adversarial Attack.}
%
Szegedy \etal~\cite{l-bfgs} find misclassification of DNN can be triggered by
an imperceptible adversarial perturbation to the input image.
%
Ian \etal~\cite{fgsm} attribute the reason to DNN being locally linear with
respect to the adversarial perturbation.
%
Subsequent first-order gradient-based methods can compromise the DNNs more
effectively under the white-box assumption~\cite{i-fgsm,madry,apgd}.
%
In contrast, black-box attacks have been explored by query-based
methods~\cite{nes-atk,spsa-atk} and transferability-based
methods~\cite{di-fgsm}, which are more practical for real-world scenarios.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to security implications of adversarial vulnerability, adversarial
	robustness of deep metric learning models has to be improved.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing defenses dismiss the min-max adversarial training, but instead
	learn from a weak adversary inefficiently.
	% our starting point
	Conversely, we propose Hardness Manipulation to efficiently perturb the
	training triplet till a specified level of hardness for adversarial
	training, according to a harder benign triplet or a pseudo-hardness
	function.
	% merit
	It is flexible since regular training and min-max adversarial training
	are its boundary cases.
	% GA Adversary
	Besides, Gradual Adversary, a family of pseudo-hardness functions is
	proposed to gradually increase the specified hardness level during training
	for a better balance between performance and robustness.
	% Intra-Class Structure
	Additionally, an Intra-Class Structure loss term among benign and adversarial
	examples further improves model robustness and efficiency.
	% Experiment and Conclusion
	Comprehensive experimental results suggest that the proposed method,
	although simple in its form, overwhelmingly outperforms the
	state-of-the-art defenses in terms of robustness, training efficiency,
	as well as performance on benign examples.
%
\end{abstract}

@@

Existing defense methods~\cite{advrank,robrank} are adversarial training-based,
inspired by Madry's \emph{min-max} adversarial training~\cite{madry} because it
is consistently one of the most effective methods for classification task.
%
Specifically, Madry's method involves a inner problem to \emph{maximize} the
loss by perturbing the inputs into adversarial examples, and an outer problem
to \emph{minimize} the loss by updating the model parameters.
%
However, in order to avoid model collapse due to excessively hard examples, the
existing DML defenses refrain from directly adopting such min-max paradigm, but
instead replace the inner problem to indirectly increase the loss value to a
certain level, which suffers from low efficiency and weak adversary (and hence
weak robustness).
%
Since training cost is already a serious issue of adversarial training, the
efficiency in gaining higher adversarial robustness under a lower budget is
inevitable and important for DML defense.

@@

\textbf{Adversarial Attack.}
%
Szegedy \etal~\cite{l-bfgs} find misclassification of DNN can be triggered by
an imperceptible adversarial perturbation to the input image.
%
Ian \etal~\cite{fgsm} attribute the reason to DNN being locally linear with
respect to the adversarial perturbation.
%
Subsequent first-order gradient-based methods can compromise the DNNs more
effectively under the white-box assumption~\cite{i-fgsm,madry,apgd,lafeat}.
%
In contrast, black-box attacks have been explored by query-based
methods~\cite{nes-atk,spsa-atk} and transferability-based
methods~\cite{di-fgsm}, which are more practical for real-world scenarios.
